Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-15 paper.qmd
Updated Figure 2

scurve_proj1_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

@@

scurve_proj2_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

@@

scurve_proj3_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

>>>>

limits <- 1
rng <- range(projected)
projected <- projected/max(abs(rng))
colnames(projected) <- c("P1", "P2")
projected <- data.frame(projected)
obs_labels <- as.character(1:nrow(training_data_scurve))

axis_scale <- 2 * limits/3
axis_pos <- -0.5 * limits

axis_labels <- colnames(training_data_scurve |> select(-ID))
rownames(axes) <- axis_labels

scurve_proj1_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50")

@@

limits <- 1
rng <- range(projected)
projected <- projected/max(abs(rng))
colnames(projected) <- c("P1", "P2")
projected <- data.frame(projected)
obs_labels <- as.character(1:nrow(training_data_scurve))

axis_scale <- 2 * limits/3
axis_pos <- -0.5 * limits

axis_labels <- colnames(training_data_scurve |> select(-ID))
rownames(axes) <- axis_labels

scurve_proj2_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50")

@@

limits <- 1
rng <- range(projected)
projected <- projected/max(abs(rng))
colnames(projected) <- c("P1", "P2")
projected <- data.frame(projected)
obs_labels <- as.character(1:nrow(training_data_scurve))

axis_scale <- 2 * limits/3
axis_pos <- -0.5 * limits

axis_labels <- colnames(training_data_scurve |> select(-ID))
rownames(axes) <- axis_labels

scurve_proj3_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50")
